Bayesian statistics and swine flu

### 2009-09-25 docs/pandemic/bayesPandemic.rnw
pandemicresults
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@416 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{frame}[fragile]
\frametitle{Fitting the model}
(to the simulated data)
<<mcmcResults,echo=true,fig=false>>=
scale = mcmcScale(params, 0.075,minScale = 0.05 )
paramSample = mcmcPandemic(data,params,priors,sigma=scale,runs=100, thin = 5)

@@

\begin{frame}[fragile]
\frametitle{With rising and falling incidence}
{\scriptsize
<<hospLoad2,echo=T,height=2,width=4>>=
# generate hospital times
Ninfect=	c(seq(1, 100, len=20),seq(100, 1, len=20), rep(2, 40) ) )

>>>>

\begin{frame}[fragile]
\frametitle{Fitting the model}
(to the simulated data)
<<mcmcResults,echo=true,fig=false>>=
scale = mcmcScale(params, 0.075,minScale = 0.05 )
paramSample = mcmcPandemic(data,params,priors,sigma=scale,runs=500, thin = 10)

@@

\begin{frame}[fragile]
\frametitle{With rising and falling incidence}
{\scriptsize
<<hospLoad2,echo=T,height=2,width=4>>=
# generate hospital times
Ninfect=c(seq(1, 100, len=20),seq(100, 1, len=20), rep(2, 40) )
